---
title: Comparison of Versions of NLSY97 Kinship Links
date: "Date: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: 4
    toc_float: true
    number_sections: true
---

This report covers the analyses used in development of the NLSY Behavior Genetics kinship links ([Joseph Rodgers](https://www.vanderbilt.edu/psychological_sciences/bio/joe-rodgers), PI).

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show',
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 4,
  fig.height   = 4,
  fig.path     = 'figure-png/'
)

echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/archive-comparison-97/archive-comparison-97.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=message_chunks}
```

<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd
#   that doesn't live in the codebehind R file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```

# Summary {.tabset .tabset-fade .tabset-pills}

## Notes
1. The current report compares the versions of the NLSY97 Links
    * Version `r olderVersionNumber`: `r olderDescription`.
    * Version `r newerVersionNumber`: `r newerDescription`.

# Comparison of Agreement
```{r graph-roc, echo=echo_chunks, message=message_chunks, fig.width=3.2, fig.height=1.5}
```

# Table of *R* Assignments
```{r table-marginal, echo=echo_chunks, message=message_chunks, results='asis'}
```

# Breakdown of Agreements 
```{r table-conditional, echo=echo_chunks, message=message_chunks, results='asis'}
```

# By Roster 

The designation of "lower" and "upper" is fairly arbitrary.  It's collapsed so a brother-sister pair contribute to the same row as a sister-brother pair.

```{r by-roster, echo=echo_chunks, message=message_chunks, results='asis'}
```



# Session Information
For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
}
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
